### 2021-02-13 evaluation.tex
Clarify the role of baselines

The final evaluation is performed on $\ProblemsVal$.
For each problem $P \in \ProblemsVal$,
a precedence is generated by the trained recommender
and Vampire is run using this precedence.
The results are averaged over 5 runs to reduce the effect of noise in the computation wall clock time.

>>>>

The final evaluation is performed on $\ProblemsVal$.
For each problem $P \in \ProblemsVal$,
a precedence is generated by the trained recommender
and Vampire is run using this precedence and a wall clock time limit of 10 seconds.
The results are averaged over 5 runs to reduce the effect of noise due to wall clock time limit.
As a baseline, the performance of Vampire with the \texttt{frequency} precedence heuristic was evaluated
with the same time limit.
